OptiFit: a fast method for fitting amplicon sequences to existing OTUs

### 2021-06-24 paper/paper.Rmd
Cite ggtext

We implemented the analysis workflow in Snakemake [@koster_snakemake_2012] and
wrote scripts in R [@r_core_team_r_2020], Python [@van_rossum_python_2009], and
GNU bash [@noauthor_bash_nodate].
Software used includes mothur v1.45.0 [@schloss_introducing_2009], VSEARCH
v2.13.3 [@rognes_vsearch_2016], numpy [@harris_array_2020], the Tidyverse
metapackage [@wickham_welcome_2019], R Markdown [@xie_r_2018], the SRA toolkit
[@noauthor_sra-tools_nodate], and the conda environment manager
[@noauthor_anaconda_2016].
The complete workflow, manuscript, and conda environment are available at
**TODO: UPDATED REPO LINK**.

>>>>

We implemented the analysis workflow in Snakemake [@koster_snakemake_2012] and
wrote scripts in R [@r_core_team_r_2020], Python [@van_rossum_python_2009], and
GNU bash [@noauthor_bash_nodate].
Software used includes mothur v1.45.0 [@schloss_introducing_2009], VSEARCH
v2.13.3 [@rognes_vsearch_2016], numpy [@harris_array_2020], the tidyverse
metapackage [@wickham_welcome_2019], R Markdown [@xie_r_2018], ggtext
[@wilke_ggtext_2020], the SRA toolkit [@noauthor_sra-tools_nodate], and the
conda environment manager [@noauthor_anaconda_2016].
The complete workflow, manuscript, and conda environment are available at
**TODO: UPDATED REPO LINK**.
